Long groovy title goes here

### 2013-06-22 shanghai.tex
Fix etale typo

To see why this is so, consider the category \cdef{$\CS_0(G)$} of pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$ and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$ are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}. Let $b : {\bar G} \to G$ be base change (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$). The proof of Proposition~\ref{prop:pullback} adapts (simplifies, in fact) to show that  $b^* : \CS_0(G) \to \CS(G)$ is a monoidal functor. This functor is fully faithful; see \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will show that $b^*$ is essentially surjective.

@@

\begin{proposition}\label{prop:etale}
If $G$ is a commutative group scheme etale over $\Fq$ and $G(\bFq)$ is finitely generated then there is a canonical isomorphism 
\[
\CS(G)_{/\text{iso}} \longrightarrow H^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EE^\times)),
\qquad \text{given by}\qquad
[\cs{L}] \mapsto [t_\cs{L}],
\]
where $t_\cs{L}: \Weil(\bFq/\Fq)\to \Hom_\text{grp}(G(\bFq),\EE^\times)$ is a cocycle such that 
\[
\forall g\in G(\Fq), \qquad t_\cs{L}(\Frob)(g) = t^\Frob_\cs{L}(g).
\]
\end{proposition}

>>>>

To see why this is so, consider the category \cdef{$\CS_0(G)$} of pairs $(\cs{L}_0,\mu_0)$ where $\cs{L}_0$ is a local system on $G$ and $\mu_0: m^*\cs{L}_0 \to \cs{L}_0 \boxtimes \cs{L}_0$ satisfies condition \ref{CS.1} adapted to sheaves on $G$; maps in $\CS_0(G)$ are defined by the second part of condition \ref{CS.2}, {\it mutatis mutandis}. \David{Should we move this definition since it will be important elsewhere?} Let $b : {\bar G} \to G$ be base change (pull-back of $G\to \Spec{\Fq}$ along $\Spec{\bFq} \to \Spec{\Fq}$). The proof of Proposition~\ref{prop:pullback} adapts (simplifies, in fact) to show that  $b^* : \CS_0(G) \to \CS(G)$ is a monoidal functor. This functor is fully faithful; see \cite{SGA7.2}*{Expos\'e XIII} and \cite{BBD}*{Prop. 5.2.1}.  We will show that $b^*$ is essentially surjective.

@@

\begin{proposition}\label{prop:etale}
If $G$ is a commutative \'etale group scheme over $\Fq$ and $G(\bFq)$ is finitely generated then there is a canonical isomorphism 
\[
\CS(G)_{/\text{iso}} \longrightarrow H^1(\Weil(\bFq/\Fq), \Hom_\text{grp}(G(\bFq),\EE^\times)),
\qquad \text{given by}\qquad
[\cs{L}] \mapsto [t_\cs{L}],
\]
where $t_\cs{L}: \Weil(\bFq/\Fq)\to \Hom_\text{grp}(G(\bFq),\EE^\times)$ is a cocycle such that 
\[
\forall g\in G(\Fq), \qquad t_\cs{L}(\Frob)(g) = t^\Frob_\cs{L}(g).
\]
\end{proposition}
